My title

### 2024-04-19 paper/paper.qmd
extra stuff

---
title: "My title"
author: 
  - Carl Fernandes
thanks: "Code and data are available at: https://github.com/Carl-1506/Happiness-and-inequality.git"
date: today
date-format: long
abstract: "This study investigates the connection between income inequality and national hapiness, questioning the impact of the Gini index. By examining cross-sectional data we find that income inequality has a limited direct effect on happiness. It is evident that factors like the quality of institutions and levels of development as measured by the Democracy Index and the Inequality adjusted Human Development Index (IHDI) have a more significant impact on shaping happiness. Our results indicate that focusing solely on income inequality doesn't provide a complete understanding. Instead a wider range of indicators are. This research contributes to the conversation on disparity and satisfaction by emphasizing the importance of using multifaceted approaches in happiness research and policy development."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Global discourse on well-being has increasingly recognized happiness as a critical indicator of societal progress. This paper embarks on an empirical inquiry into the determinants of happiness, with a particular focus on income distribution. Traditional economic theories suggest a correlation between economic prosperity and happiness, but emerging research prompts a re-evaluation of this association. In this context, income inequality, typically measured by the Gini index, emerges as a potential factor influencing happiness. Yet, the depth of its impact remains under-examined and is often overshadowed by more visible economic indicators.

@@

Our analysis is based on a range of literature that explores the connection, between gaps and personal well being. A key focus of our framework is the research by @oishi2011income who argue for a relationship between income inequality and individual happiness. They suggest that perceptions of fairness and levels of trust play a role in shaping this connection. Particularly they highlight that individuals with incomes tend to be less happy when faced with inequality not necessarily because of their own earnings but due to reduced trust and fairness perceptions. Their results indicate that how people subjectively experience inequality can be just as significant as the income gaps.

On the hand @meyer2013consumption present a perspective on inequality compared to the mainstream discussions. Their study during the Recession reveals a contrast; while income inequality increased consumption inequality showed a different trend. This contrast prompts a look at measures of inequality stressing the importance of exploring other aspects of economic experiences like spending habits when assessing their impact, on happiness. Our research focuses on exploring if income inequality, by itself can predict happiness or if its impact depends on socio factors, like trust, fairness, consumption levels and the quality of democratic governance. The model we use aims to separate these interconnected influences emphasizing that a complete view of happiness goes beyond measures.

@@

The paper proceeds as follows: Section 2 presents a review of the pertinent literature, laying the groundwork for our empirical strategy. In Section 3, we detail the data sources and describe the variables under study. Section 4 outlines our methodology, articulating the econometric approach and data handling procedures. Section 5, the core of our empirical analysis, presents the results and explores their robustness. Section 6 discusses the implications of our findings within the broader socio-economic context, and Section 7 concludes by synthesizing the study's insights and suggesting avenues for future research.

The remainder of this paper is structured as follows. @sec-data....

# Literature Reivew

@@

# Model

@@

# Results

@@

# Discussion

@@

# Conclusion

>>>>

---
title: "My title"
author: 
  - Carl Fernandes
thanks: "Code and data are available at: https://github.com/Carl-1506/Happiness-and-inequality.git"
date: today
date-format: long
abstract: "This study explores the connection between income inequality and national hapiness, questioning the impact of the Gini index. By examining cross-sectional data we find that income inequality has a limited direct effect on happiness. It is evident that factors like the quality of institutions and levels of development as measured by the Democracy Index and the Inequality adjusted Human Development Index (IHDI) have a more significant impact on shaping happiness. Our results indicate that focusing solely on income inequality doesn't provide a complete understanding. Instead a wider range of indicators are. This research contributes to the conversation on disparity and satisfaction by emphasizing the importance of using multifaceted approaches in happiness research and policy development."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Global discourse on well-being has increasingly recognized happiness as a critical indicator of societal progress. This paper examines the determinants of happiness, with a particular focus on income distribution. Traditional economic theories suggest a correlation between economic equality and happiness, but emerging research prompts a re-evaluation of this association. In this context, income inequality, typically measured by the Gini index, emerges as a potential factor influencing happiness. Yet, the depth of its impact remains under-examined and is often overshadowed by more visible economic indicators.

@@

Our analysis is based on a range of literature that explores the connection between economic inequality and personal well being. A key focus of our framework is the research by @oishi2011income who argue for a relationship between income inequality and individual happiness. They suggest that perceptions of fairness and levels of trust play a role in shaping this connection. Particularly they highlight that individuals with incomes tend to be less happy when faced with inequality not necessarily because of their own earnings but due to reduced trust and fairness perceptions. Their results indicate that how people subjectively experience inequality can be just as significant as the income gaps.

On the hand @meyer2013consumption present a perspective on inequality compared to the mainstream discussions. Their study during the Recession reveals a contrast; while income inequality increased consumption inequality showed a different trend. This contrast prompts a look at measures of inequality stressing the importance of exploring other aspects of economic experiences like spending habits when assessing their impact on happiness. Our research focuses on exploring if income inequality by itself can predict happiness or if its impact depends on other socio-economic factors like trust, fairness, consumption levels and the quality of democratic governance. The model we use aims to separate these interconnected influences emphasizing that a complete view of happiness goes beyond measures.

@@

The paper proceeds as follows: @sec-lit presents a review of the pertinent literature, laying the groundwork for our empirical strategy. In @sec-data, we detail the data sources and describe the variables under study. @sec-model outlines our models. @sec-results, the core of our empirical analysis, presents the results and explores their robustness. @sec-dis discusses the implications of our findings within the broader socio-economic context, and @sec-con concludes by synthesizing the study's insights and suggesting avenues for future research.

# Literature Reivew {#sec-lit}

@@

# Model {#sec-model}

@@

# Results {#sec-results}

@@

# Discussion {#sec-dis}

@@

# Conclusion {#sec-con}
